---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bigdataclass

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/edgararuiz/bigdataclass.svg?branch=master)](https://travis-ci.com/edgararuiz/bigdataclass)
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/bigdataclass/branch/master/graph/badge.svg)](https://codecov.io/gh/edgararuiz/bigdataclass?branch=master)
<!-- badges: end -->

The goal of `bigdataclass` is to provide an easy way to create the data and materials needed for the Big Data with R class.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/bigdataclass")
```
## Setup the class locally 

1. Load the package
    ```{r}
    library(bigdataclass)
    ```

1. Run `bdc_init_class_local()` to create the class in a folder called **big-data-class**
    ```{r, eval = FALSE}
    bdc_create_class()
    ```


## Setup on a server with an external database

### Build time

#### Needed R packages

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r}
library(bigdataclass)
cat(paste0(bdc_utils_libraries(), collapse = "\n"))
```


#### Setup the database and create the exercise files

1. Connect to the database *(replace with actual user name and password)*
    ```{r, eval = FALSE}
    library(DBI)
    
    con <- dbConnect(RPostgres::Postgres(),
                     host = "localhost",
                     user = "admin_user",
                     port = 5432,
                     password = "password", 
                     dbname = "postgres",
                     bigint = "integer"
                     )
    ```

1. Run the following script
    ```{r, eval = FALSE}
    ## Load the library
    library(bigdataclass)
    ## Path to where the files are to be saved
    folder <- "usr/share/class"
    ## Creates the "retail" schema inside the database connection
    con <- bdc_db_init(con)
    ## Creates the tables and views inside the schema
    bdc_db_tables(con = con, avg_daily_orders = 10000)
    ## Builds the files and saves them to the path in "folder" 
    bdc_data_files(con = con, folder = file.path(folder, "files"))
    ## Downloads the books from the Gutenbergh API and saves them to the "folder"
    bdc_data_books(file.path(folder, "books"))
    ```
